## Course: Visual Analytics for Policy and Management
###Multivariate Exercise 3
####Isabella Sun


####Figures:

1. [Exercise 1: Descriptive Plot](#ex1)

2. [Exercise 2: Inferential Plot](#ex2)

##
bring in the data and load the necessary packages. Information on safety in 60 cities: digital, health, infrastructure, and personal

```{r}
library(openxlsx)
link2="https://github.com/EvansDataScience/data/raw/master/safeCitiesIndex.xlsx"

safe2=read.xlsx(link2)

library(ggplot2)
library(GGally)
library(reshape)
library(ggiraph)
library(ggiraphExtra)
library(dotwhisker)
library(broom)
library(dplyr)
```

###Descriptive Plot
Create data to plot and order from smallest to largest ranking across 4 dimenssions of safety
```{r}
safe2x=safe2

safe2x$min=apply(safe2x[,c(2:5)],1,min)

safe2x$min=rank(safe2x$min,ties.method ='first' )

cityRk=as.factor(safe2x[order(safe2x$min),]$city)

safe2x$city=factor(safe2x$city,
                   levels= cityRk,
                   labels = cityRk,
                   ordered = T)

safe2x$min=NULL
```

misc figure elements
```{r}
title_radar = "Digital, Health, Infrastructure, and Personal Safety in 60 Cities"
source = "Source: Safe Cities Index"
```
<a id='ex1'></a>
```{r, fig.width=18, fig.height=20}
base = ggRadar(safe2x,aes(group='city'),legend.position="none") 

plot1 = base + facet_wrap(~city,ncol = 6) + labs(title = title_radar,
                    x =NULL, 
                    y = NULL,
                    caption = source) + 
                    theme(plot.caption = element_text(hjust = 0, size = 20),
                        plot.title = element_text(hjust = 0.5, size = 20))

plot1 
```

###Inferential Plot

calculating regression models and transforming then in a way that ggplot can read
```{r}
model1=lm(PERSONAL~HEALTH+INFRASTRUCTURE,data=safe2[,-1])
model1_t = tidy(model1) %>%   # we save the result as a tidy object and...
    mutate(model = "Model 1") # we add a column 'model' with values 'Model 1'

model2=lm(PERSONAL~.,data=safe2[,-1]) # ~. means: all the remaining variables
model2_t <- tidy(model2) %>% mutate(model = "Model 2")

allModels=rbind(model1_t, model2_t)

```

misc plot elements
```{r}
reg_title = "Infrastructure and Digital Safety are Statistically Significantly Associated
with an Increase in Personal Safety"

```

```{r}

dwplot(allModels) + 
    geom_vline(xintercept = 0, 
               colour = "grey60", 
               linetype = 2) +
    scale_colour_grey(start = .1, end = .7) + theme(legend.title=element_blank(),  plot.title = element_text(size = 10)) + labs(title = reg_title, caption = source)

```

